Subsegmental language detection in Celtic language text

### 2014-05-08 codeswitch-cltw-2014/codeswitch.tex
some more
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52639 72bbbca6-d526-0410-a7d9-f06f51895060

\section{Introduction}
\label{intro}
With the increase in multilingualism and the adoption of ‘another’ acceptable language apart from the usual creates a change in the data. This change can be looked upon as bad when we are faced with the burden of upgrading systems to adapt to it, on the other hand such change is 
unavoidable and has to be welcomed. The good part is that the user or the speaker feels more comfortable in expressing their opinions. Such change directly requires us to upgrade our current systems \cite{fung2008multilingual} so that the processing or the analysis of the data is in no way compromised.\\
   Such code switching is more common in less formal ways of communication like on chats, forums and social media. Our motivation is to build a detection scheme which can sub-segment such sentences to the primary and secondary language tags and then prepare this to be processed further by modules which make use of this information to analyse useful information from this data. Specially in the case of languages like Irish, Breton and Welsh where the native speakers are very less, these people reach out to others and most of their posts are code-switched. Rather than promoting research based on monolingual technologies we would like to adopt to the trend and try to help other researchers in understanding this data in a better way.
\cite{lyu2006}

%
% The following footnote without marker is needed for the camera-ready
% version of the paper.
% Comment out the instructions (first text) and uncomment the 8 lines
% under "final paper" for your variant of English.
% 
\blfootnote{
    %
    % for review submission
    %
    \hspace{-0.65cm}  % space normally used by the marker
    Place licence statement here for the camera-ready version, see
    Section~\ref{licence} of the instructions for preparing a
    manuscript.
    %
    % % final paper: en-uk version (to license, a licence)
    %
    % \hspace{-0.65cm}  % space normally used by the marker
    % This work is licensed under a Creative Commons 
    % Attribution 4.0 International Licence.
    % Page numbers and proceedings footer are added by
    % the organisers.
    % Licence details:
    % \url{http://creativecommons.org/licenses/by/4.0/}
    % 
    % % final paper: en-us version (to licence, a license)
    %
    % \hspace{-0.65cm}  % space normally used by the marker
    % This work is licenced under a Creative Commons 
    % Attribution 4.0 International License.
    % Page numbers and proceedings footer are added by
    % the organizers.
    % License details:
    % \url{http://creativecommons.org/licenses/by/4.0/}
}

>>>>

\section{Introduction}
\label{intro}
With the increase in multilingualism and the adoption of ‘another’ acceptable language apart from the usual creates a change in the data. This change can be looked upon as bad when we are faced with the burden of upgrading systems to adapt to it, on the other hand such change is 
unavoidable and has to be welcomed. The good part is that the user or the speaker feels more comfortable in expressing their opinions. Such change directly requires us to upgrade our current systems \cite{fung2008multilingual} so that the processing or the analysis of the data is in no way compromised.\\
   Such code switching is more common in less formal ways of communication like on chats, forums and social media. Our motivation is to build a detection scheme which can sub-segment such sentences to the primary and secondary language tags and then prepare this to be processed further by modules which make use of this information to analyse useful information from this data. Specially in the case of languages like Irish, Breton and Welsh where the native speakers are very less, these people reach out to others and most of their posts are code-switched. Rather than promoting research based on monolingual technologies we would like to adopt to the trend and try to help other researchers in understanding this data in a better way.
   In Ireland, and the surrounding areas a significant number of speakers use Welsh, Breton, Irish, English and French. About 14.6\% of the population of Wales considers themselves to be fluent in Welsh(2011) \footnote{http://ons.gov.uk/ons/rel/census/2011-census/key-statistics-for-unitary-authorities-in-wales/stb-2011-census-key-statistics-for-wales.html#tab---Proficiency-in-Welsh}. In the Republic of Ireland 94,000 people use it as a primary language outside the education system \footnote{http://www.cso.ie/en/media/csoie/census/documents/census2011pdr/Pdf\%208\%20Tables.pdf}. It is noticed that the Irish and the Welsh people often use English with their respective languages while they code-switch while Bretons have a natural French influence. Hence, in our experiments we plan to analyse the results for code switching and detection of segments in the following bilingual pairs - Welsh-English, Irish-English and Breton-French,  thus identifying the primary and secondary languages in the data.
\cite{lyu2006}

%
% The following footnote without marker is needed for the camera-ready
% version of the paper.
% Comment out the instructions (first text) and uncomment the 8 lines
% under "final paper" for your variant of English.
%

\blfootnote{
    %
    % for review submission
    %
    \hspace{-0.65cm}  % space normally used by the marker
    Place licence statement here for the camera-ready version, see
    Section~\ref{licence} of the instructions for preparing a
    manuscript.
    %
    % % final paper: en-uk version (to license, a licence)
    %
    % \hspace{-0.65cm}  % space normally used by the marker
    % This work is licensed under a Creative Commons 
    % Attribution 4.0 International Licence.
    % Page numbers and proceedings footer are added by
    % the organisers.
    % Licence details:
    % \url{http://creativecommons.org/licenses/by/4.0/}
    % 
    % % final paper: en-us version (to licence, a license)
    %
    % \hspace{-0.65cm}  % space normally used by the marker
    % This work is licenced under a Creative Commons 
    % Attribution 4.0 International License.
    % Page numbers and proceedings footer are added by
    % the organizers.
    % License details:
    % \url{http://creativecommons.org/licenses/by/4.0/}
}
